\begin{thebibliography}{999}
    \bibitem{architecting_spacecraft}Friedenthal, S. \& Oster, C. Architecting spacecraft with SysML.  (2017)
    \bibitem{nasa_handbook}NASA NASA System Engineering Handbook Revision 2. (NASA,2020), https://www.nasa.gov/connect/ebooks/nasa-systems-engineering-handbook
    \bibitem{asundi13_cubes}Asundi, S. \& Fitz-Coy, N. CubeSat mission design based on a systems engineering approach. {\em 2013 IEEE Aerospace Conference}. pp. nil (2013,3), http://dx.doi.org/10.1109/AERO.2013.6496900
    \bibitem{scitech_proceeding}Sean Marquez, S. Model-Based CubeSat Flight-Software Architecture using a Docs-as-Code approach. {\em AIAA Scitech Conference 2023}. (2023,1), https://arc.aiaa.org/doi/10.2514/6.2023-1126
    \bibitem{cds_rev14}The CubeSat Program, C. CubeSat Design Specification Rev. 14. (The CubeSat Program, Cal Poly SLO,2022)
    \bibitem{sealion_cdr}Academy, O. Critical Design Review: Mission SeaLion - ODU/CGA 3U CubeSat.  (2022)
    \bibitem{heidt_new}Heidt, H., Puig-Suari, J., Moore, A., Nakasuka, S. \& Twiggs, R. CubeSat - A new generation of picosatellite for education and industry low-cost space experimentation. {\em AIAA/USU Annual Conference On Small Satellites, 12th, Utah State University, Logan; UNITED STATES; 21-24 Aug.2000}. (2000,8), https://www.proquest.com/conference-papers-proceedings/cubesat-new-generation-picosatellite-education/docview/27219077/se-2
    \bibitem{sealion_cdr}Academy, O. Critical Design Review: Mission SeaLion - ODU/CGA 3U CubeSat.  (2022)
    \bibitem{heidt_new}Heidt, H., Puig-Suari, J., Moore, A., Nakasuka, S. \& Twiggs, R. CubeSat - A new generation of picosatellite for education and industry low-cost space experimentation. {\em AIAA/USU Annual Conference On Small Satellites, 12th, Utah State University, Logan; UNITED STATES; 21-24 Aug.2000}. (2000,8), https://www.proquest.com/conference-papers-proceedings/cubesat-new-generation-picosatellite-education/docview/27219077/se-2
    \bibitem{swartwout_data}Swartwout, M. CubeSat Database.  (2021), https://sites.google.com/a/slu.edu/swartwout/cubesat-database
    \bibitem{pumpkin_cubesat}Shop, C. Pumpkin CubeSat Kits.  (2023,3), https://www.cubesatshop.com/product/pumpkin-cubesat-kits/
    \bibitem{cubesat_handbook}Cappelletti Cubesat handbook: From mission design to operations. (Elsevier Science \& Technology,2020)
    \bibitem{reliving_24}Swartwout, M. Reliving 24 Years in the Next 12 Minutes: A Statistical and Personal History of University-Class Satellites.  (2018), https://digitalcommons.usu.edu/cgi/viewcontent.cgi?article=4277\&context=smallsat
    \bibitem{aalto}Praks AALTO-1 earth observation cubesat mission — Educational outcomes. {\em IEEE International Geoscience And Remote Sensing Symposium (IGARSS)}. (2015)
    \bibitem{howtosetup}Berthoud, M. How to Set Up a CubeSat Project - Preliminary Survey Results. {\em 30th Annual AIAA/USU Conference On Small Satellites}. (2016)
    \bibitem{sealion_mission_architecture}Team, S. SeaLion Mission Architecture. (Old Dominion University,2022), https://github.com/ODU-CGA-CubeSat/sealion-mission-architecture
    \bibitem{caesar_model_based_approach}David Wagner CAESAR Model-Based Approach to Harness Design. {\em Proceedings Of IEEE Aerospace Conference}. (2020,3)
    \bibitem{ibm_mbse}Brown, B. Model-based systems engineering: Revolution or evolution?.  (2011,12)
    \bibitem{call_herber_2022}Call, D. \& Herber, D. Applicability of the diffusion of innovation theory to accelerate model-based systems engineering adoption. {\em Systems Engineering}. \textbf{25}, 574-583 (2022)
    \bibitem{younse_cameron_bradley_2021}Younse, P., Cameron, J. \& Bradley, T. Comparative analysis of model-based and traditional systems engineering approaches for architecting a robotic space system through Automatic Information Transfer. {\em IEEE Access}. \textbf{9} pp. 107476-107492 (2021)
    \bibitem{mazzini}Mazzini, S., Tronci, E., Paccagnini, C. \& Olive, X. A Model-Based methodology to support the Space System Engineering (MBSSE). {\em ERTS2 2010, Embedded Real Time Software \& Systems}. (2010,5), https://hal.science/hal-02267836
    \bibitem{esa}ESA Model-based system engineering. , https://www.esa.int/Enabling\_Support/Preparing\_for\_the\_Future/Discovery\_and\_Preparation/Model-based\_system\_engineering
    \bibitem{nottage_corns_2012}Nottage, D. \& Corns, S. Application of model-based systems engineering on a university satellite design team. {\em Procedia Computer Science}. \textbf{8} pp. 207-213 (2012)
    \bibitem{kaslow}Kaslow, D., Ayres, B., Cahill, P., Hart, L. \& Yntema, R. Developing a CubeSat Model-Based System Engineering (MBSE) reference model — Interim status \#3. {\em 2017 IEEE Aerospace Conference}. pp. 1-15 (2017)
    \bibitem{docs_as_code}Holscher, E. Docs as Code.  (2022), https://www.writethedocs.org/guide/docs-as-code/
    \bibitem{structurizr}Structurizr Software architecture models as code. {\em Structurizr}., https://structurizr.org/
    \bibitem{f_prime_prime}Bocchino, R., Levison, J. \& Starch, M. FPP: A Modeling Language for F Prime. {\em 2022 IEEE Aerospace Conference (AERO)}. pp. 1-15 (2022)
    \bibitem{f_prime}NASA F' a flight software and embedded systems framework. {\em F'}., https://nasa.github.io/fprime/
    \bibitem{mach30_git}Simmons, J. Mach30 Modeling Language. (Mach30 Foundation,2022), https://github.com/Mach30/m30ml
    \bibitem{sys_ml}Partners, S. SysML Specifications.  (2023), https://sysml.org/sysml-specs/
    \bibitem{sys_ml2}Submission Team, S. SysML-v2-Release.  (2023), https://github.com/Systems-Modeling/SysML-v2-Release
    \bibitem{plantuml}PlantUML PlantUML.  (2023), https://plantuml.com/
    \bibitem{oml_language}Maged Elaasar, N. Ontological Modeling Language: Origin and Rationale.  (2022), http://www.opencaesar.io/oml/
    \bibitem{oml_origin_and_rationale}Jenkinis, S. Ontological Modeling Language 1.4.  (2022), http://www.opencaesar.io/imce/2021/06/19/OML-Origin-and-Rationale.html
    \bibitem{linkml}Mungall, C. LinkML model your data. {\em LinkML}., https://linkml.io/
    \bibitem{sealion_dof}Team, S. Extension of the Distributed OSHW Framework (DOF) for Modeling CubeSats. (Old Dominion University,2023), https://odu-cga-cubesat.github.io/dof-cubesat/
    \bibitem{sealion_page}Team, S. SeaLion Mission Architecture. (Old Dominion University,2023), https://odu-cga-cubesat.github.io/sealion-mission-architecture/
\end{thebibliography}